---
title: "RA NK project start"
author: "Rebecca Amodeo & Nina Kerkebane"
date: "2/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)



```

## Project Overview
 Start here:
Team Nina
  - has university data (price per year over 200 years; enrollment by in- vs out-of-state and associated prices, ethnicity ratios; gender ratios retention rates)
  - her project: impact of tuition increases on enrollment levels of low-income students
  - predict? price of tuition based on prev year's prices
  - predict? enrollment rates based on price issues (by group?)
  - predict? retention rates based on price issues (by group?)
  - predict? minority enrollment based on other school culture factors such as majority white (or difference in school composition by race and local community racial composition) etc .

Ed Says:
  - used (time, instution, etc?) fixed effects and time series data 
  - predict retention OR predict who will leave (numbers of them, who will be the leavers?)


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
